\documentclass[11pt]{article}


\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\fancyfoot[L]{Project X' \\ CST 200}
\fancyfoot[C]{Proposal Worksheet \\ {\copyright} Preston Lee 2010. All rights reserved.}
\fancyfoot[RO, LE] {{\thepage} of \pageref{LastPage}}


\title{Project X'}

\author{Preston Lee}
\date{}

\begin{document}
\maketitle
\tableofcontents


\section{Abstract}
Everyone is generally pleased with Project X progress. Unfortunately, external factotrs have pushed management into restructuring the project. Effective immediately, approximately 25\% of the class will be ``laid off" from their current teams. (Will be announced.) {\it Life must go on.}

{\bf Each team must complete and submit this proposal document. It must be approved by the instructor.}

\pagebreak


\section{Change.}
All dismissed developers (announced) must immediately join a different, pre-existing team, bound by the restrictions as the original project. No new teams may be created. {\it (Reminder: 4 people per team, maximum.)}

Each team {\it must} elect a new captain using the same original restrictions, even if the original captain survived the layoffs.

\subsection{Leadership.}

Decide upon a new team captain, and specify him/her below:

\vspace{1cm}
\hspace{.5in}{\bf Team: }

\hspace{.5in}{\bf Old Team Captain: }

\hspace{.5in}{\bf New Team Captain: }
\vspace{1cm}

\subsection{Functional enhancements.}

Project X' will not only continue the functional development of the original software, but take you through the packaging and distribution of the software, as well. (Consider this an opportunity to build your personal development portfolio.) 

\subsection{Demonstrate your knowledge.}

For your X' proposal to be approved, your project {\bf must} prove your knowledge of course material by demonstrating {\it all} of the following, {\bf in addition to} the criteria of the original project:

\begin{description}
\item[Test] Demonstrate at least 70\% test coverage of non-GUI code. (In other words, you need to {\it prove} you are testing.) 
\item[Enhancement] Make no less than {\bf two significant functional enhancements} to the software. This may be in addition to the original specs, or completion of items that were scope cut.
\item[Package] Create a distributable package of your choosing--via a .jar, .exe installer, JNLP or other common mechanism.
\item[Document] A brief ``Users' Guide" must be provided, approximately two pages, documenting how to install, run and use the software.
\item[Release] You must release your completed product via the world wide web. I will download and run the software as you specify in your documentation.
\end{description}

\subsection{Milestones.}
The team will need to hit all of the following milestones for full credit.

\begin{description}
\item[\bf Thursday, October 28th] Proposals due.
\item[\bf Tuesday, November 2nd] Last chance acceptance date. 
\item[\bf Thursday, December 2nd] Submission, demo and presentation. Your team--lead by the captain--will deliver a well rehearsed project presentation and application demonstration in front of the class.
\end{description}


\pagebreak

\section{Define success.}
Team members will receive {\it individual} grades for their project contributions. Additionally, the team captain will deliver a live 10-15 minute demo in front of the class prior to grading.

\subsection{Grading breakdown.}

Total points possible: 36. (Tip: This is a lot, so take the project seriously.)



\begin{description}
\item[30\%] Given by instructor, based on the previously defined criteria.
\item[30\%] Defined by your team, below.
\item[20\%] Peer review.
\item[20\%] In-class demo. {\it Be prepared.} Be professional. Quality of content, delivery and project demo will be considered. In other words, make sure your project doesn't ``blow up" in front of the class! You will have projector access to show slides, code, and other additional resources you deem fit. 
\end{description}


\subsection{Custom grading criteria.}

Define at least four {\bf new}, specific ways your project should be graded. (For example: {\it ``Correctly retrieves automated Google search results"}, or {\it ``Renders MineSweeper board correctly."}) These must be reasonably challenging criteria for a team of 3-4 people given over a month of development time. Trivial criteria such as {\it ``Application accepts invalid user input without crashing."} will be rejected.


\end{document}
